---
title: "gas test"
editor: visual
format:
  html:
    embed-resources: true
    toc: true
    code-fold: true
---

# Gas Concentration and Feature Analysis

This analysis examines the relationship between **gas concentration** and each measured feature in the dataset. Each plot shows concentration on the x-axis and the selected feature on the y-axis, with observations coloured by `gas_class`.

The jittered points make it easier to see individual observations, while the linear trend line provides a simple visual indication of the relationship between concentration and the feature.

The same plotting procedure is applied to every feature in the dataset so that the features can be compared consistently.

## Concentration vs Feat 1

The following plot shows the relationship between gas concentration and `feat_1`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_1, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 1", x = "Concentration", y = "Feat 1")

ggplotly(p)
```

## Concentration vs Feat 2

The following plot shows the relationship between gas concentration and `feat_2`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_2, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 2", x = "Concentration", y = "Feat 2")

ggplotly(p)
```

## Concentration vs Feat 3

The following plot shows the relationship between gas concentration and `feat_3`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_3, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 3", x = "Concentration", y = "Feat 3")

ggplotly(p)
```

## Concentration vs Feat 4

The following plot shows the relationship between gas concentration and `feat_4`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_4, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 4", x = "Concentration", y = "Feat 4")

ggplotly(p)
```

## Concentration vs Feat 5

The following plot shows the relationship between gas concentration and `feat_5`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_5, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 5", x = "Concentration", y = "Feat 5")

ggplotly(p)
```

## Concentration vs Feat 6

The following plot shows the relationship between gas concentration and `feat_6`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_6, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 6", x = "Concentration", y = "Feat 6")

ggplotly(p)
```

## Concentration vs Feat 7

The following plot shows the relationship between gas concentration and `feat_7`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_7, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 7", x = "Concentration", y = "Feat 7")

ggplotly(p)
```

## Concentration vs Feat 8

The following plot shows the relationship between gas concentration and `feat_8`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_8, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 8", x = "Concentration", y = "Feat 8")

ggplotly(p)
```

## Concentration vs Feat 9

The following plot shows the relationship between gas concentration and `feat_9`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_9, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 9", x = "Concentration", y = "Feat 9")

ggplotly(p)
```

## Concentration vs Feat 10

The following plot shows the relationship between gas concentration and `feat_10`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_10, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 10", x = "Concentration", y = "Feat 10")

ggplotly(p)
```

## Concentration vs Feat 11

The following plot shows the relationship between gas concentration and `feat_11`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_11, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 11", x = "Concentration", y = "Feat 11")

ggplotly(p)
```

## Concentration vs Feat 12

The following plot shows the relationship between gas concentration and `feat_12`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_12, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 12", x = "Concentration", y = "Feat 12")

ggplotly(p)
```

## Concentration vs Feat 13

The following plot shows the relationship between gas concentration and `feat_13`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_13, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 13", x = "Concentration", y = "Feat 13")

ggplotly(p)
```

## Concentration vs Feat 14

The following plot shows the relationship between gas concentration and `feat_14`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_14, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 14", x = "Concentration", y = "Feat 14")

ggplotly(p)
```

## Concentration vs Feat 15

The following plot shows the relationship between gas concentration and `feat_15`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_15, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 15", x = "Concentration", y = "Feat 15")

ggplotly(p)
```

## Concentration vs Feat 16

The following plot shows the relationship between gas concentration and `feat_16`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_16, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 16", x = "Concentration", y = "Feat 16")

ggplotly(p)
```

## Concentration vs Feat 17

The following plot shows the relationship between gas concentration and `feat_17`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_17, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 17", x = "Concentration", y = "Feat 17")

ggplotly(p)
```

## Concentration vs Feat 18

The following plot shows the relationship between gas concentration and `feat_18`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_18, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 18", x = "Concentration", y = "Feat 18")

ggplotly(p)
```

## Concentration vs Feat 19

The following plot shows the relationship between gas concentration and `feat_19`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_19, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 19", x = "Concentration", y = "Feat 19")

ggplotly(p)
```

## Concentration vs Feat 20

The following plot shows the relationship between gas concentration and `feat_20`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_20, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 20", x = "Concentration", y = "Feat 20")

ggplotly(p)
```

## Concentration vs Feat 21

The following plot shows the relationship between gas concentration and `feat_21`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_21, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 21", x = "Concentration", y = "Feat 21")

ggplotly(p)
```

## Concentration vs Feat 22

The following plot shows the relationship between gas concentration and `feat_22`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_22, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 22", x = "Concentration", y = "Feat 22")

ggplotly(p)
```

## Concentration vs Feat 23

The following plot shows the relationship between gas concentration and `feat_23`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_23, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 23", x = "Concentration", y = "Feat 23")

ggplotly(p)
```

## Concentration vs Feat 24

The following plot shows the relationship between gas concentration and `feat_24`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_24, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 24", x = "Concentration", y = "Feat 24")

ggplotly(p)
```

## Concentration vs Feat 25

The following plot shows the relationship between gas concentration and `feat_25`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_25, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 25", x = "Concentration", y = "Feat 25")

ggplotly(p)
```

## Concentration vs Feat 26

The following plot shows the relationship between gas concentration and `feat_26`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_26, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 26", x = "Concentration", y = "Feat 26")

ggplotly(p)
```

## Concentration vs Feat 27

The following plot shows the relationship between gas concentration and `feat_27`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_27, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 27", x = "Concentration", y = "Feat 27")

ggplotly(p)
```

## Concentration vs Feat 28

The following plot shows the relationship between gas concentration and `feat_28`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_28, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 28", x = "Concentration", y = "Feat 28")

ggplotly(p)
```

## Concentration vs Feat 29

The following plot shows the relationship between gas concentration and `feat_29`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_29, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 29", x = "Concentration", y = "Feat 29")

ggplotly(p)
```

## Concentration vs Feat 30

The following plot shows the relationship between gas concentration and `feat_30`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_30, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 30", x = "Concentration", y = "Feat 30")

ggplotly(p)
```

## Concentration vs Feat 31

The following plot shows the relationship between gas concentration and `feat_31`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_31, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 31", x = "Concentration", y = "Feat 31")

ggplotly(p)
```

## Concentration vs Feat 32

The following plot shows the relationship between gas concentration and `feat_32`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_32, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 32", x = "Concentration", y = "Feat 32")

ggplotly(p)
```

## Concentration vs Feat 33

The following plot shows the relationship between gas concentration and `feat_33`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_33, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 33", x = "Concentration", y = "Feat 33")

ggplotly(p)
```

## Concentration vs Feat 34

The following plot shows the relationship between gas concentration and `feat_34`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_34, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 34", x = "Concentration", y = "Feat 34")

ggplotly(p)
```

## Concentration vs Feat 35

The following plot shows the relationship between gas concentration and `feat_35`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_35, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 35", x = "Concentration", y = "Feat 35")

ggplotly(p)
```

## Concentration vs Feat 36

The following plot shows the relationship between gas concentration and `feat_36`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_36, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 36", x = "Concentration", y = "Feat 36")

ggplotly(p)
```

## Concentration vs Feat 37

The following plot shows the relationship between gas concentration and `feat_37`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_37, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 37", x = "Concentration", y = "Feat 37")

ggplotly(p)
```

## Concentration vs Feat 38

The following plot shows the relationship between gas concentration and `feat_38`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_38, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 38", x = "Concentration", y = "Feat 38")

ggplotly(p)
```

## Concentration vs Feat 39

The following plot shows the relationship between gas concentration and `feat_39`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_39, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 39", x = "Concentration", y = "Feat 39")

ggplotly(p)
```

## Concentration vs Feat 40

The following plot shows the relationship between gas concentration and `feat_40`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_40, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 40", x = "Concentration", y = "Feat 40")

ggplotly(p)
```

## Concentration vs Feat 41

The following plot shows the relationship between gas concentration and `feat_41`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_41, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 41", x = "Concentration", y = "Feat 41")

ggplotly(p)
```

## Concentration vs Feat 42

The following plot shows the relationship between gas concentration and `feat_42`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_42, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 42", x = "Concentration", y = "Feat 42")

ggplotly(p)
```

## Concentration vs Feat 43

The following plot shows the relationship between gas concentration and `feat_43`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_43, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 43", x = "Concentration", y = "Feat 43")

ggplotly(p)
```

## Concentration vs Feat 44

The following plot shows the relationship between gas concentration and `feat_44`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_44, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 44", x = "Concentration", y = "Feat 44")

ggplotly(p)
```

## Concentration vs Feat 45

The following plot shows the relationship between gas concentration and `feat_45`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_45, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 45", x = "Concentration", y = "Feat 45")

ggplotly(p)
```

## Concentration vs Feat 46

The following plot shows the relationship between gas concentration and `feat_46`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_46, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 46", x = "Concentration", y = "Feat 46")

ggplotly(p)
```

## Concentration vs Feat 47

The following plot shows the relationship between gas concentration and `feat_47`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_47, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 47", x = "Concentration", y = "Feat 47")

ggplotly(p)
```

## Concentration vs Feat 48

The following plot shows the relationship between gas concentration and `feat_48`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_48, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 48", x = "Concentration", y = "Feat 48")

ggplotly(p)
```

## Concentration vs Feat 49

The following plot shows the relationship between gas concentration and `feat_49`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_49, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 49", x = "Concentration", y = "Feat 49")

ggplotly(p)
```

## Concentration vs Feat 50

The following plot shows the relationship between gas concentration and `feat_50`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_50, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 50", x = "Concentration", y = "Feat 50")

ggplotly(p)
```

## Concentration vs Feat 51

The following plot shows the relationship between gas concentration and `feat_51`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_51, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 51", x = "Concentration", y = "Feat 51")

ggplotly(p)
```

## Concentration vs Feat 52

The following plot shows the relationship between gas concentration and `feat_52`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_52, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 52", x = "Concentration", y = "Feat 52")

ggplotly(p)
```

## Concentration vs Feat 53

The following plot shows the relationship between gas concentration and `feat_53`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_53, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 53", x = "Concentration", y = "Feat 53")

ggplotly(p)
```

## Concentration vs Feat 54

The following plot shows the relationship between gas concentration and `feat_54`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_54, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 54", x = "Concentration", y = "Feat 54")

ggplotly(p)
```

## Concentration vs Feat 55

The following plot shows the relationship between gas concentration and `feat_55`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_55, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 55", x = "Concentration", y = "Feat 55")

ggplotly(p)
```

## Concentration vs Feat 56

The following plot shows the relationship between gas concentration and `feat_56`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_56, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 56", x = "Concentration", y = "Feat 56")

ggplotly(p)
```

## Concentration vs Feat 57

The following plot shows the relationship between gas concentration and `feat_57`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_57, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 57", x = "Concentration", y = "Feat 57")

ggplotly(p)
```

## Concentration vs Feat 58

The following plot shows the relationship between gas concentration and `feat_58`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_58, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 58", x = "Concentration", y = "Feat 58")

ggplotly(p)
```

## Concentration vs Feat 59

The following plot shows the relationship between gas concentration and `feat_59`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_59, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 59", x = "Concentration", y = "Feat 59")

ggplotly(p)
```

## Concentration vs Feat 60

The following plot shows the relationship between gas concentration and `feat_60`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_60, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 60", x = "Concentration", y = "Feat 60")

ggplotly(p)
```

## Concentration vs Feat 61

The following plot shows the relationship between gas concentration and `feat_61`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_61, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 61", x = "Concentration", y = "Feat 61")

ggplotly(p)
```

## Concentration vs Feat 62

The following plot shows the relationship between gas concentration and `feat_62`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_62, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 62", x = "Concentration", y = "Feat 62")

ggplotly(p)
```

## Concentration vs Feat 63

The following plot shows the relationship between gas concentration and `feat_63`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_63, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 63", x = "Concentration", y = "Feat 63")

ggplotly(p)
```

## Concentration vs Feat 64

The following plot shows the relationship between gas concentration and `feat_64`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_64, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 64", x = "Concentration", y = "Feat 64")

ggplotly(p)
```

## Concentration vs Feat 65

The following plot shows the relationship between gas concentration and `feat_65`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_65, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 65", x = "Concentration", y = "Feat 65")

ggplotly(p)
```

## Concentration vs Feat 66

The following plot shows the relationship between gas concentration and `feat_66`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_66, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 66", x = "Concentration", y = "Feat 66")

ggplotly(p)
```

## Concentration vs Feat 67

The following plot shows the relationship between gas concentration and `feat_67`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_67, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 67", x = "Concentration", y = "Feat 67")

ggplotly(p)
```

## Concentration vs Feat 68

The following plot shows the relationship between gas concentration and `feat_68`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_68, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 68", x = "Concentration", y = "Feat 68")

ggplotly(p)
```

## Concentration vs Feat 69

The following plot shows the relationship between gas concentration and `feat_69`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_69, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 69", x = "Concentration", y = "Feat 69")

ggplotly(p)
```

## Concentration vs Feat 70

The following plot shows the relationship between gas concentration and `feat_70`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_70, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 70", x = "Concentration", y = "Feat 70")

ggplotly(p)
```

## Concentration vs Feat 71

The following plot shows the relationship between gas concentration and `feat_71`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_71, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 71", x = "Concentration", y = "Feat 71")

ggplotly(p)
```

## Concentration vs Feat 72

The following plot shows the relationship between gas concentration and `feat_72`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_72, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 72", x = "Concentration", y = "Feat 72")

ggplotly(p)
```

## Concentration vs Feat 73

The following plot shows the relationship between gas concentration and `feat_73`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_73, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 73", x = "Concentration", y = "Feat 73")

ggplotly(p)
```

## Concentration vs Feat 74

The following plot shows the relationship between gas concentration and `feat_74`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_74, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 74", x = "Concentration", y = "Feat 74")

ggplotly(p)
```

## Concentration vs Feat 75

The following plot shows the relationship between gas concentration and `feat_75`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_75, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 75", x = "Concentration", y = "Feat 75")

ggplotly(p)
```

## Concentration vs Feat 76

The following plot shows the relationship between gas concentration and `feat_76`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_76, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 76", x = "Concentration", y = "Feat 76")

ggplotly(p)
```

## Concentration vs Feat 77

The following plot shows the relationship between gas concentration and `feat_77`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_77, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 77", x = "Concentration", y = "Feat 77")

ggplotly(p)
```

## Concentration vs Feat 78

The following plot shows the relationship between gas concentration and `feat_78`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_78, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 78", x = "Concentration", y = "Feat 78")

ggplotly(p)
```

## Concentration vs Feat 79

The following plot shows the relationship between gas concentration and `feat_79`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_79, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 79", x = "Concentration", y = "Feat 79")

ggplotly(p)
```

## Concentration vs Feat 80

The following plot shows the relationship between gas concentration and `feat_80`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_80, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 80", x = "Concentration", y = "Feat 80")

ggplotly(p)
```

## Concentration vs Feat 81

The following plot shows the relationship between gas concentration and `feat_81`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_81, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 81", x = "Concentration", y = "Feat 81")

ggplotly(p)
```

## Concentration vs Feat 82

The following plot shows the relationship between gas concentration and `feat_82`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_82, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 82", x = "Concentration", y = "Feat 82")

ggplotly(p)
```

## Concentration vs Feat 83

The following plot shows the relationship between gas concentration and `feat_83`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_83, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 83", x = "Concentration", y = "Feat 83")

ggplotly(p)
```

## Concentration vs Feat 84

The following plot shows the relationship between gas concentration and `feat_84`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_84, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 84", x = "Concentration", y = "Feat 84")

ggplotly(p)
```

## Concentration vs Feat 85

The following plot shows the relationship between gas concentration and `feat_85`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_85, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 85", x = "Concentration", y = "Feat 85")

ggplotly(p)
```

## Concentration vs Feat 86

The following plot shows the relationship between gas concentration and `feat_86`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_86, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 86", x = "Concentration", y = "Feat 86")

ggplotly(p)
```

## Concentration vs Feat 87

The following plot shows the relationship between gas concentration and `feat_87`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_87, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 87", x = "Concentration", y = "Feat 87")

ggplotly(p)
```

## Concentration vs Feat 88

The following plot shows the relationship between gas concentration and `feat_88`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_88, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 88", x = "Concentration", y = "Feat 88")

ggplotly(p)
```

## Concentration vs Feat 89

The following plot shows the relationship between gas concentration and `feat_89`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_89, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 89", x = "Concentration", y = "Feat 89")

ggplotly(p)
```

## Concentration vs Feat 90

The following plot shows the relationship between gas concentration and `feat_90`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_90, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 90", x = "Concentration", y = "Feat 90")

ggplotly(p)
```

## Concentration vs Feat 91

The following plot shows the relationship between gas concentration and `feat_91`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_91, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 91", x = "Concentration", y = "Feat 91")

ggplotly(p)
```

## Concentration vs Feat 92

The following plot shows the relationship between gas concentration and `feat_92`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_92, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 92", x = "Concentration", y = "Feat 92")

ggplotly(p)
```

## Concentration vs Feat 93

The following plot shows the relationship between gas concentration and `feat_93`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_93, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 93", x = "Concentration", y = "Feat 93")

ggplotly(p)
```

## Concentration vs Feat 94

The following plot shows the relationship between gas concentration and `feat_94`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_94, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 94", x = "Concentration", y = "Feat 94")

ggplotly(p)
```

## Concentration vs Feat 95

The following plot shows the relationship between gas concentration and `feat_95`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_95, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 95", x = "Concentration", y = "Feat 95")

ggplotly(p)
```

## Concentration vs Feat 96

The following plot shows the relationship between gas concentration and `feat_96`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_96, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 96", x = "Concentration", y = "Feat 96")

ggplotly(p)
```

## Concentration vs Feat 97

The following plot shows the relationship between gas concentration and `feat_97`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_97, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 97", x = "Concentration", y = "Feat 97")

ggplotly(p)
```

## Concentration vs Feat 98

The following plot shows the relationship between gas concentration and `feat_98`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_98, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 98", x = "Concentration", y = "Feat 98")

ggplotly(p)
```

## Concentration vs Feat 99

The following plot shows the relationship between gas concentration and `feat_99`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_99, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 99", x = "Concentration", y = "Feat 99")

ggplotly(p)
```

## Concentration vs Feat 100

The following plot shows the relationship between gas concentration and `feat_100`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_100, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 100", x = "Concentration", y = "Feat 100")

ggplotly(p)
```

## Concentration vs Feat 101

The following plot shows the relationship between gas concentration and `feat_101`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_101, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 101", x = "Concentration", y = "Feat 101")

ggplotly(p)
```

## Concentration vs Feat 102

The following plot shows the relationship between gas concentration and `feat_102`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_102, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 102", x = "Concentration", y = "Feat 102")

ggplotly(p)
```

## Concentration vs Feat 103

The following plot shows the relationship between gas concentration and `feat_103`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_103, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 103", x = "Concentration", y = "Feat 103")

ggplotly(p)
```

## Concentration vs Feat 104

The following plot shows the relationship between gas concentration and `feat_104`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_104, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 104", x = "Concentration", y = "Feat 104")

ggplotly(p)
```

## Concentration vs Feat 105

The following plot shows the relationship between gas concentration and `feat_105`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_105, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 105", x = "Concentration", y = "Feat 105")

ggplotly(p)
```

## Concentration vs Feat 106

The following plot shows the relationship between gas concentration and `feat_106`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_106, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 106", x = "Concentration", y = "Feat 106")

ggplotly(p)
```

## Concentration vs Feat 107

The following plot shows the relationship between gas concentration and `feat_107`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_107, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 107", x = "Concentration", y = "Feat 107")

ggplotly(p)
```

## Concentration vs Feat 108

The following plot shows the relationship between gas concentration and `feat_108`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_108, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 108", x = "Concentration", y = "Feat 108")

ggplotly(p)
```

## Concentration vs Feat 109

The following plot shows the relationship between gas concentration and `feat_109`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_109, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 109", x = "Concentration", y = "Feat 109")

ggplotly(p)
```

## Concentration vs Feat 110

The following plot shows the relationship between gas concentration and `feat_110`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_110, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 110", x = "Concentration", y = "Feat 110")

ggplotly(p)
```

## Concentration vs Feat 111

The following plot shows the relationship between gas concentration and `feat_111`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_111, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 111", x = "Concentration", y = "Feat 111")

ggplotly(p)
```

## Concentration vs Feat 112

The following plot shows the relationship between gas concentration and `feat_112`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_112, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 112", x = "Concentration", y = "Feat 112")

ggplotly(p)
```

## Concentration vs Feat 113

The following plot shows the relationship between gas concentration and `feat_113`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_113, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 113", x = "Concentration", y = "Feat 113")

ggplotly(p)
```

## Concentration vs Feat 114

The following plot shows the relationship between gas concentration and `feat_114`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_114, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 114", x = "Concentration", y = "Feat 114")

ggplotly(p)
```

## Concentration vs Feat 115

The following plot shows the relationship between gas concentration and `feat_115`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_115, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 115", x = "Concentration", y = "Feat 115")

ggplotly(p)
```

## Concentration vs Feat 116

The following plot shows the relationship between gas concentration and `feat_116`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_116, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 116", x = "Concentration", y = "Feat 116")

ggplotly(p)
```

## Concentration vs Feat 117

The following plot shows the relationship between gas concentration and `feat_117`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_117, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 117", x = "Concentration", y = "Feat 117")

ggplotly(p)
```

## Concentration vs Feat 118

The following plot shows the relationship between gas concentration and `feat_118`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_118, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 118", x = "Concentration", y = "Feat 118")

ggplotly(p)
```

## Concentration vs Feat 119

The following plot shows the relationship between gas concentration and `feat_119`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_119, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 119", x = "Concentration", y = "Feat 119")

ggplotly(p)
```

## Concentration vs Feat 120

The following plot shows the relationship between gas concentration and `feat_120`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_120, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 120", x = "Concentration", y = "Feat 120")

ggplotly(p)
```

## Concentration vs Feat 121

The following plot shows the relationship between gas concentration and `feat_121`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_121, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 121", x = "Concentration", y = "Feat 121")

ggplotly(p)
```

## Concentration vs Feat 122

The following plot shows the relationship between gas concentration and `feat_122`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_122, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 122", x = "Concentration", y = "Feat 122")

ggplotly(p)
```

## Concentration vs Feat 123

The following plot shows the relationship between gas concentration and `feat_123`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_123, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 123", x = "Concentration", y = "Feat 123")

ggplotly(p)
```

## Concentration vs Feat 124

The following plot shows the relationship between gas concentration and `feat_124`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_124, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 124", x = "Concentration", y = "Feat 124")

ggplotly(p)
```

## Concentration vs Feat 125

The following plot shows the relationship between gas concentration and `feat_125`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_125, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 125", x = "Concentration", y = "Feat 125")

ggplotly(p)
```

## Concentration vs Feat 126

The following plot shows the relationship between gas concentration and `feat_126`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_126, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 126", x = "Concentration", y = "Feat 126")

ggplotly(p)
```

## Concentration vs Feat 127

The following plot shows the relationship between gas concentration and `feat_127`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_127, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 127", x = "Concentration", y = "Feat 127")

ggplotly(p)
```

## Concentration vs Feat 128

The following plot shows the relationship between gas concentration and `feat_128`. The observations are coloured according to gas class, allowing differences between gas classes to be visually compared.

```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(plotly)

my_data <- read_csv("/Users/sebastian/Downloads/train_version_1.csv")

p <- ggplot(my_data, aes(x = concentration, y = feat_128, color = as.factor(gas_class))) +
  geom_jitter(width = 1, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, by = 100)) +
  labs(title = "Concentration vs Feat 128", x = "Concentration", y = "Feat 128")

ggplotly(p)
```
